---
title: "Australian Coverage"
author: "Fonti Kar"
date: "2022-10-23"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(plotly, tidyverse, datapasta, scales)


IA_theme <- function() {
  theme(text = element_text(family = "Avenir"),
        axis.title = element_text(family = "Avenir",
                                  size = 12),
        #small tick marks
        axis.text = element_text(family = "Avenir",
                                 size = 12),
        legend.title = element_text(family = "Avenir",
                                    size = 12,
                                    colour = "black"),
        legend.text = element_text(family = "Avenir",
                                   size = 12,
                                   colour = "black"),
        legend.key = element_rect(fill = "#F5F5F1", color = NA),
        legend.position = "bottom",
        legend.justification = "centre",
        legend.background = element_rect(fill = "#F5F5F1", color = NA), 
        #panel is where you datapoints are
        panel.background = element_rect(fill = "#F5F5F1", color = NA),
        panel.grid.major = element_line(colour = "white"),
        panel.grid.minor = element_blank(),
        #area outside the panel
        plot.title = element_blank(),
        plot.background = element_rect(fill = "#F5F5F1", color = NA))
}
```

## Aims

- Create a visualization to show how 'complete' our invertebrate taxa are, i.e. apparently people are pretty sure we know all the odonates, but only 50% of the Leps.
- I want the graphic to point people toward taxa that we CAN be sure of and work with and not write things off as probably unknown if it's actually part of a really well-known group. 
- I think it would be cool to be able to say [all these] Orders can be monitored, etc because they're well understood and then ‘although these Orders are thought to have another 20,000 species to describe, [all these] Families are well described' or whatever. . 
- Australia only
- First Phylum 
- Then Order

## Read in data

```{r}
phyla <- read_csv("data/phyla_how_complete.csv")

phyla |> rename(describe = `Described species in Australia`,
                estimated = `Estimated species in Australia`,
                endemic = `endemic%`) -> phyla

phyla |> print(n =57)
```

### Data cleaning

```{r}
phyla |> filter(group == "inv") -> inv

inv |> arrange(phylum, -describe, -estimated) -> inv_ordered

inv_ordered <- inv_ordered |>
  mutate(phylum_plot = ifelse(common_name == "Other Invertebrates","Other Invertebrates", phylum))  

inv_nested <- inv_ordered |> mutate(class = ifelse(class == phylum, NA, class),
                      class = ifelse(class %in% c("Molluscs", "Onycophora", 
                                                  "Nematodes", "Echinoderms", 
                                                  "Cnidarians", "Annelids", "Other Invertebrates"),NA, class)) 

# Create % described
inv_nested |> mutate(percent_desc = (describe/estimated)*100) -> inv_per

# Exclude NA percent
inv_per |> drop_na(percent_desc) -> complete_per

complete_per |> mutate(percent_desc = round(percent_desc, digits = 2)) -> complete_per

```

## Descriptive stats

```{r}
unique(inv_nested$phylum) |> vector_paste()
unique(inv_nested$class) |> vector_paste()
c(NA, "Insecta", "Crustacea", "Arachnida", "Myriapoda", "Hexapoda", "Pycnogonida", "Tunicata", "Cephalochordata")
c("Acanthocephala", "Annelida", "Arthropoda", "Chordata", "Cnidaria", "Echindodermata", "Hemichordata", "Mollusca", "Nematoda", "Onychophora", "Other", "Platyhelminthes", "Porifera")

# Total described
sum(inv_nested$describe)

# Total Arthropod describe
sum(inv_nested[inv_nested$phylum == "Arthropoda","describe"])

# Total Chordata described
sum(inv_nested[inv_nested$phylum == "Chordata","describe"])
```

# Plotly

### Plain
```{r}
 plot_ly(
  labels = c("Australian Invertebrates", "Acanthocephala", "Annelida", 
             "Arthropoda", "Insecta", "Crustacea", "Arachnida", "Myriapoda", "Hexapoda", "Pycnogonida",
             "Chordata", "Tunicata", "Cephalochordata",
             "Cnidaria", "Echindodermata", "Hemichordata", "Mollusca", 
             "Nematoda", "Onychophora", "Other", "Platyhelminthes", "Porifera"),
   parents = c("", "Australian Invertebrates", "Australian Invertebrates", 
              "Australian Invertebrates", "Arthropoda", "Arthropoda", "Arthropoda", "Arthropoda", "Arthropoda", "Arthropoda",
              "Australian Invertebrates", "Chordata", "Chordata",
              "Australian Invertebrates", "Australian Invertebrates","Australian Invertebrates","Australian Invertebrates",
              "Australian Invertebrates","Australian Invertebrates","Australian Invertebrates","Australian Invertebrates","Australian Invertebrates"),
  type = 'sunburst'
)

```

### Described species

```{r}
plot_ly(
  labels = c("Australian Invertebrates", "Acanthocephala", "Annelida",
             "Arthropoda", "Insecta", "Crustacea", "Arachnida", "Myriapoda", "Hexapoda", "Pycnogonida",
             "Chordata", "Tunicata", "Cephalochordata",
             "Cnidaria", "Echindodermata", "Hemichordata", "Mollusca", 
             "Nematoda", "Onychophora", "Other", "Platyhelminthes", "Porifera"),
  parents = c("", "Australian Invertebrates", "Australian Invertebrates",
              "Australian Invertebrates", "Arthropoda", "Arthropoda", "Arthropoda", "Arthropoda", "Arthropoda", "Arthropoda",
            "Australian Invertebrates", "Chordata", "Chordata",
            "Australian Invertebrates", "Australian Invertebrates","Australian Invertebrates","Australian Invertebrates",
              "Australian Invertebrates","Australian Invertebrates","Australian Invertebrates","Australian Invertebrates","Australian Invertebrates"),
  values = c(sum(inv_nested$describe), inv_nested$describe[1:2],
             sum(inv_nested[inv_nested$phylum == "Arthropoda","describe"]), inv_nested$describe[3:8], 
             sum(inv_nested[inv_nested$phylum == "Chordata","describe"]), inv_nested$describe[9:10],
             inv_nested$describe[11:19]),
  
  type = 'sunburst'
)
```

### Estimated species

```{r}
plot_ly(
  labels = c("Australian Invertebrates", "Acanthocephala", "Annelida",
             "Arthropoda", "Insecta", "Crustacea", "Arachnida", "Myriapoda", "Hexapoda", "Pycnogonida",
             "Chordata", "Tunicata", "Cephalochordata",
             "Cnidaria", "Echindodermata", "Hemichordata", "Mollusca", 
             "Nematoda", "Onychophora", "Other", "Platyhelminthes", "Porifera"),
  parents = c("", "Australian Invertebrates", "Australian Invertebrates",
              "Australian Invertebrates", "Arthropoda", "Arthropoda", "Arthropoda", "Arthropoda", "Arthropoda", "Arthropoda",
            "Australian Invertebrates", "Chordata", "Chordata",
            "Australian Invertebrates", "Australian Invertebrates","Australian Invertebrates","Australian Invertebrates",
              "Australian Invertebrates","Australian Invertebrates","Australian Invertebrates","Australian Invertebrates","Australian Invertebrates"),
  values = c(sum(inv_nested$estimated, na.rm = TRUE), inv_nested$estimated[1:2],
             sum(inv_nested[inv_nested$phylum == "Arthropoda","estimated"], na.rm = TRUE), inv_nested$estimated[3:8], 
             sum(inv_nested[inv_nested$phylum == "Chordata","estimated"], na.rm = TRUE), inv_nested$estimated[9:10],
             inv_nested$estimated[11:19]),
  
  type = 'sunburst'
)
```

### Percent described

```{r}
plot_ly(
  labels = c("Australian Invertebrates", "Acanthocephala", "Annelida",
             "Arthropoda", "Insecta", "Crustacea", "Arachnida", "Myriapoda", "Hexapoda",
             "Chordata", "Tunicata", "Cephalochordata",
             "Cnidaria", "Echindodermata", "Hemichordata", "Mollusca", 
             "Nematoda", "Onychophora", "Other", "Platyhelminthes", "Porifera"),
  parents = c("", "Australian Invertebrates", "Australian Invertebrates",
              "Australian Invertebrates", "Arthropoda", "Arthropoda", "Arthropoda", "Arthropoda", "Arthropoda",
            "Australian Invertebrates", "Chordata", "Chordata",
            "Australian Invertebrates", "Australian Invertebrates","Australian Invertebrates","Australian Invertebrates",
              "Australian Invertebrates","Australian Invertebrates","Australian Invertebrates","Australian Invertebrates","Australian Invertebrates"),
  values = c(sum(complete_per$percent_desc, na.rm = TRUE), complete_per$percent_desc[1:2],
             sum(complete_per[complete_per$phylum == "Arthropoda","percent_desc"], na.rm = TRUE), complete_per$percent_desc[3:7], 
             sum(complete_per[complete_per$phylum == "Chordata","percent_desc"], na.rm = TRUE), complete_per$percent_desc[8:9],
             complete_per$percent_desc[10:18]),
  
  type = 'sunburst'
)
```


# Simple bar plot

## Phylum

```{r}
complete_per %>% 
  pivot_longer(cols = describe:estimated, names_to = "count_type", values_to = "species") -> complete_per_longer
  
complete_per_longer %>% 
  group_by(common_name, count_type) %>% 
  summarise(species = sum(species)) %>% 
  ungroup() -> complete_per_longer_summary

# complete_per_longer %>% 
#   group_by(phylum_plot, count_type) %>% 
#   summarise(species = sum(species)) %>% 
#   ungroup() -> complete_per_longer_summary

common_name_stack <- complete_per_longer_summary

# Fix long names
common_name_stack$common_name[5] <- "Insects, Crabs, \n Spiders and Millipedes"
common_name_stack$common_name[6] <- "Insects, Crabs, \n Spiders and Millipedes"

# Arrange stacked bars from low to high
# Trick the stacked bars
common_name_stack %>% 
  pivot_wider(names_from = count_type, values_from = species) %>% 
  mutate(percent_described = (describe/estimated)*100,
         remaining_unknown = estimated - describe, 
         common_name_total = paste(common_name, "\n",estimated, "species")) %>% 
  select(common_name, common_name_total, percent_described, describe, estimated) %>% 
  pivot_longer(values_to = 'species', names_to = "count_type", cols = 4:5) -> common_name_absolute_with_percent

# Main plot
main_phylum <- 
common_name_absolute_with_percent %>% 
  mutate(
    count_type = fct_relevel(count_type, "estimated", "describe"),
    common_name_total = fct_reorder(common_name_total, desc(species))) %>% 
  ggplot(aes(x = common_name_total, y = species, fill = count_type)) + 
  geom_bar(stat = "identity", position = position_dodge(), alpha = 0.8) + 
  xlab("Phylum") + 
  ylab("Number of Species") + 
  scale_y_continuous(limits = c(0, 270000), 
                     breaks = scales::breaks_extended(7),
                     labels = scales::label_comma()) + 
  scale_fill_manual(values = c("#db9880", "#8D9BBC"),  
                    labels=c('Described species', 'Estimated species'),
                    breaks=c('describe', 'estimated')) +
  guides(fill=guide_legend(title="")) +
  labs(caption = "(based on data from Chapman (2009) Numbers of Living Species in Australia and the World)") + 
  coord_flip() + 
  theme_minimal() + 
  IA_theme()  
  annotate("text", y = 15000, x = "Other Invertebrates \n 6055 species", label = "53%", family = "Avenir", size = 5) + 
  annotate("text", y = 19000, x = "Flat Worms \n 10000 species", label = "15.9%", family = "Avenir", size = 5) + 
  annotate("text", y = 22000, x = "Snails, Squid and Clams \n 12250 species", label = "71.0%", family = "Avenir", size = 5) + 
  annotate("text", y = 40500, x = "Round Worms \n 30000 species", label = "6.87%", family = "Avenir", size = 5) +
  annotate("text", y = 260500, x = "Insects, Crabs, \n Spiders and Millipedes \n 251008 species", label = "30.6%", family = "Avenir", size = 5) +
  annotate("text", y = 12000, x = "Velvet Worms \n 80 species", label = "88.8%", family = "Avenir", size = 5) + 
  annotate("text", y = 12000, x = "Seastars and Urchins \n 2000 species", label = "73.8%", family = "Avenir", size = 5) + 
  annotate("text", y = 15000, x = "Corals and Jellies \n 2200 species", label = " 77.5%", family = "Avenir", size = 5) + 
  annotate("text", y = 15000, x = "Sponges \n 3500 species", label = "42.2%", family = "Avenir", size = 5) + 
  annotate("text", y = 15000, x = "Segmented Worms \n 4230 species", label = "51.8%", family = "Avenir", size = 5)

ggsave("output/main_phylum", device = cairo_pdf, width = 12, height = 8)
  
```

### Inset
```{r}

# Groups with < 10K taxa
common_name_absolute_with_percent %>% 
  filter(species <= 10000,
         !common_name %in% c("Snails, Squid and Clams", "Round Worms", "Flat Worms", "Other Invertebrates")) -> lessthan10k

inset <- 
lessthan10k %>% 
  mutate(
    count_type = fct_relevel(count_type, "estimated", "describe"),
    common_name = fct_reorder(common_name, desc(species))) %>% 
  ggplot(aes(x = common_name, y = species, fill = count_type)) + 
  geom_bar(stat = "identity", position = position_dodge(), alpha = 0.8) + 
  scale_y_continuous(limits = c(0, 4600), 
                     labels = scales::label_comma()) + 
  xlab("") + 
  ylab("") + 
  scale_fill_manual(values = c("#db9880", "#8D9BBC"),  
                    labels=c('Described species', 'Estimated species'),
                    breaks=c('describe', 'estimated')) + 
  coord_flip() + 
  theme_minimal() + 
  IA_theme() +
  theme(legend.position = "none") + 
  annotate("text", y = 300, x = "Velvet Worms", label = "88.8%", family = "Avenir", size = 5) + 
  annotate("text", y = 2280, x = "Seastars and Urchins", label = "73.8%", family = "Avenir", size = 5) + 
  annotate("text", y = 2450, x = "Corals and Jellies", label = " 77.5%", family = "Avenir", size = 5) + 
  annotate("text", y = 3800, x = "Sponges", label = "42.2%", family = "Avenir", size = 5) + 
  annotate("text", y = 4450, x = "Segmented Worms", label = "51.8%", family = "Avenir", size = 5)
    

### Put it altogether
main_phylum + inset_element(inset, 0.2, 0.4, 1, 1)
```

# Stacked bar plot

### Phylum
```{r}
# Arrange stacked bars from low to high
# Trick the stacked bars
common_name_stack %>% 
  pivot_wider(names_from = count_type, values_from = species) %>% 
  mutate(percent_described = (describe/estimated)*100,
         remaining_unknown = estimated - describe,
         percent_unknown = (remaining_unknown/estimated)*100) %>% 
  select(common_name, percent_described, percent_unknown, describe, -estimated, remaining_unknown) %>% 
  pivot_longer(values_to = 'species', names_to = "count_type", cols = 4:5) -> common_name_stack_with_percent

# Make the main plot
common_name_stack_with_percent %>% 
  mutate(count_type = fct_relevel(count_type, "remaining_unknown", "describe"),
         common_name = fct_reorder(common_name, desc(percent_described))) %>%
  ggplot(aes(fill=count_type, y=species, x=common_name)) + 
  geom_bar(position="fill", stat="identity") + 
  scale_fill_manual(values = c("#db9880", "#8D9BBC"),  
                    labels=c('Described species', 'Estimated species'),
                    breaks=c('describe', 'remaining_unknown')) +
  scale_y_continuous(labels = scales::label_percent(accuracy = 1)) + 
  guides(fill=guide_legend(title="")) +
  xlab("Phylum") + 
  ylab("Percentage  of Total Estimated Number of Species") + 
  labs(caption = "(based on data from Chapman (2009) Numbers of Living Species in Australia and the World)") + 
  coord_flip() +
  IA_theme() -> stacked_phylum_p
  
# Annotate with percentages known
stacked_phylum_p + 
  annotate("text", y = 0.035, x = "Round Worms", label = "6.87%", family = "Avenir", size = 4, colour = "white") +
  annotate("text", y = 0.035, x = "Flat Worms", label = "15.9%", family = "Avenir", size = 4, colour = "white") +
  annotate("text", y = 0.035, x = "Insects, Crabs, \n Spiders and Millipedes", label = " 30.6%", family = "Avenir", size = 4.5, colour = "white") + 
  annotate("text", y = 0.035, x = "Sponges", label = "42.2%", family = "Avenir", size = 4, colour = "white") +
  annotate("text", y = 0.035, x = "Segmented Worms", label = "51.8%", family = "Avenir", size = 4, colour = "white") + 
  annotate("text", y = 0.035, x = "Other Invertebrates", label = "53%", family = "Avenir", size = 4, colour = "white") + 
  annotate("text", y = 0.035, x = "Snails, Squid and Clams", label = "71%", family = "Avenir", size = 4, colour = "white") + 
  annotate("text", y = 0.035, x = "Seastars and Urchins", label = "73.8%", family = "Avenir", size = 4, colour = "white") +
  annotate("text", y = 0.035, x = "Corals and Jellies", label = "77.5%", family = "Avenir", size = 4, colour = "white") + 
  annotate("text", y = 0.035, x = "Velvet Worms", label = "88.8%", family = "Avenir", size = 4, colour = "white") -> stacked_phylum_percent


# Annotate with percent unknown
stacked_phylum_percent + 
  annotate("text", y = 0.95, x = "Round Worms", label = "93.1%", family = "Avenir", size = 4, color = "white") + 
  annotate("text", y = 0.95, x = "Flat Worms", label = "84.1%", family = "Avenir", size = 4, color = "white") +
  annotate("text", y = 0.95, x = "Insects, Crabs, \n Spiders and Millipedes", label = "69.4%", family = "Avenir", size = 4, color = "white") +
  annotate("text", y = 0.95, x = "Sponges", label = "57.8%", family = "Avenir", size = 4, color = "white") +
  annotate("text", y = 0.95, x = "Segmented Worms", label = "48.2%", family = "Avenir", size = 4, color = "white") + 
  annotate("text", y = 0.95, x = "Other Invertebrates", label = "47%", family = "Avenir", size = 4, color = "white") + 
  annotate("text", y = 0.95, x = "Snails, Squid and Clams", label = "29%", family = "Avenir", size = 4, color = "white") + 
  annotate("text", y = 0.95, x = "Seastars and Urchins", label = "26.2", family = "Avenir", size = 4, color = "white") +
  annotate("text", y = 0.95, x = "Corals and Jellies", label = "22.5%", family = "Avenir", size = 4, color = "white") + 
  annotate("text", y = 0.95, x = "Velvet Worms", label = "11.2%", family = "Avenir", size = 4, color = "white")
  

# Annotate with total described species
stacked_phylum_percent + 
  annotate("text", y = 0.92, x = "Round Worms", label = "6,055 species", family = "Avenir", size = 4, color = "white") + 
  annotate("text", y = 0.92, x = "Flat Worms", label = "10,000 species", family = "Avenir", size = 4, color = "white") +
  annotate("text", y = 0.92, x = "Insects, Crustaceans,\n Chelicerates and Myriapods", label = "251,008 species", family = "Avenir", size = 4, color = "white") +
  annotate("text", y = 0.92, x = "Sponges", label = "3,500 species", family = "Avenir", size = 4, color = "white") +
  annotate("text", y = 0.92, x = "Segmented Worms", label = "4,230 species", family = "Avenir", size = 4, color = "white") + 
  annotate("text", y = 0.92, x = "Other Invertebrates", label = "6,055 species", family = "Avenir", size = 4, color = "white") + 
  annotate("text", y = 0.92, x = "Snails, Squid and Clams", label = "12,250 species", family = "Avenir", size = 4, color = "white") + 
  annotate("text", y = 0.92, x = "Seastars and Urchins", label = "2,000 species", family = "Avenir", size = 4, color = "white") +
  annotate("text", y = 0.92, x = "Corals and Jellies", label = "2,200 species", family = "Avenir", size = 4, color = "white") + 
  annotate("text", y = 0.943, x = "Velvet Worms", label = "80 species", family = "Avenir", size = 4, color = "white")
  
  
```


#### Class

```{r}
complete_per %>% 
  filter(!is.na(class)) %>% 
  pivot_longer(cols = describe:estimated, names_to = "count_type", values_to = "species") -> class_data_longer

class_data_longer %>% 
  group_by(class, count_type) %>% 
  summarise(species = sum(species)) %>% 
  ungroup() -> class_longer_summary


class_longer_summary %>% 
  filter(! class %in% c("Cephalochordata")) %>% 
  mutate(count_type = fct_relevel(count_type, "estimated", "describe")) %>% 
  ggplot(aes(x = reorder(class, desc(species)), y = species, fill = count_type)) + 
  geom_bar(stat = "identity", position = position_dodge(), alpha = 0.8) + 
  xlab("Class") + 
  ylab("Number of Species") + 
  scale_fill_manual(values = c("#db9880", "#8D9BBC"),
                      labels=c('Estimated species', 'Described species')) +
  guides(fill=guide_legend(title="")) +
  labs(caption = "(based on data from Chapman (2009) Numbers of Living Species in Australia and the World)") +
  coord_flip() + 
  theme_minimal() + 
  IA_theme()
```

#### Crop circles

```{r}
# https://images.ala.org.au/image/details?imageId=
# 
# https://ala-images.s3.ap-southeast-2.amazonaws.com/store/5/a/9/2/5e4bbf48-8752-48b4-8224-a90c7eeee362

images <- paste0(file.path("images/"), list.files("images/"))
df <- tibble(class = c("Arachnida","Crustacea", "Insecta", "Myriapoda", "Tunicata"), 
             images = images) %>% 
  mutate(images_cropped = circle_crop(images))

class_longer_summary %>% 
  mutate(count_type = fct_relevel(count_type, "estimated", "describe")) %>% 
  filter(! class %in% c("Cephalochordata", "Hexapoda")) %>% 
  left_join(df, by = "class") -> class_longer_summary

class_longer_summary %>%
  mutate(image_cropped = ifelse(count_type == "estimated",NA,images_cropped),
         class = reorder(class, desc(species)),
         value = species + (40000)) -> class_data_final


class_data_final %>% 
  ggplot(aes(x = class, y = species, fill = count_type)) + 
  geom_bar(stat = "identity", position = position_dodge(), alpha = 0.8) + 
  geom_image(aes(y = value , image = image_cropped), size = .15) + 
  xlab("Class") + 
  ylab("Number of Species") + 
  ylim(c(0,220000)) +
  scale_fill_manual(values = c("#db9880", "#8D9BBC"),
                      labels=c('Estimated species', 'Described species')) +
  guides(fill=guide_legend(title="")) +
  labs(caption = "(based on data from Chapman (2009) Numbers of Living Species in Australia and the World)") +
  coord_flip() + 
  theme_minimal() + 
  IA_theme()
```



### A bubble plot

```{r}
complete_per %>% 
ggplot(aes(x = describe, y = estimated, size = percent_desc, colour = phylum)) + 
  geom_point(alpha = 0.5) + 
  scale_size(range = c(2,10), name="Percent of species described") + 
  guides(colour = guide_legend(title = "Phylum")) +
  xlab("Number of species described") + 
  ylab("Number of estimated species") +
  scale_x_log10(label = label_log()) +
  scale_y_log10(label = label_log()) +
  theme_minimal()
```

### Order factor levels of Phylum

```{r}
complete_per %>% 
    mutate(phylum = fct_relevel(phylum, 
            "Acanthocephala", "Annelida", "Arthropoda", 
            "Chordata", "Cnidaria", "Echindodermata", 
            "Hemichordata", "Mollusca", "Nematoda", "Onychophora", "Platyhelminthes", "Porifera", "Other")) -> complete_per_2

complete_per_2 %>% 
ggplot(aes(x = describe, y = estimated, size = percent_desc, colour = phylum)) + 
  geom_point(alpha = 0.5) + 
  scale_size(range = c(2,10), name="Percent of species described") + 
  guides(colour = guide_legend(title = "Phylum")) +
  xlab("Number of species described") + 
  ylab("Number of estimated species") +
  scale_x_log10(label = label_log()) +
  scale_y_log10(label = label_log()) +
  theme_minimal()
```

### An IA colour palette

```{r}
#In order of
levels(complete_per_2$phylum)

scale_colour_manual(values = c("#db9880", "#8D9BBC", "#B298BB", 
                               "#f0dd56", "#9ad9d1", "##B38177",
                               "#e5cb14", "#A3B28D", "#465577",
                               "#9aa3b6", "#606672", "#d0b2c9"))
```

### Get some text on the bubbles

```{r}
complete_per_2 %>% 
ggplot(aes(x = describe, y = estimated)) + 
  geom_point(aes(size = percent_desc, colour = phylum), alpha = 0.5) + 
  scale_size(range = c(2,10), name="Percent of species described") + 
  guides(colour = guide_legend(title = "Phylum")) +
  geom_text(aes(label = phylum), colour = "black", 
            nudge_x = -0.2, size = 3) +
  xlab("Number of species described") + 
  ylab("Number of estimated species") +
  scale_x_log10(label = label_log()) +
  scale_y_log10(label = label_log()) +
  theme_minimal()
```

```{r}
#importing fonts
#if you are using extrafont
font_import() #press y + Enter to add fonts
fonttable()
#if you are using sysfont & showtext
font_add_google("Montserrat")
showtext_auto()
```


### An IA theme

We need 14 colours

```{r}
IA_theme <- function() {
  theme(axis.title = element_text(family = "Montserrat",
                                  size = 12),
        #small tick marks
        axis.text = element_text(family = "Montserrat",
                                 size = 12),
        legend.title = element_text(family = "Montserrat",
                                    size = 12,
                                    colour = "black"),
        legend.text = element_text(family = "Montserrat",
                                   size = 12,
                                   colour = "black"),
        legend.key = element_rect(fill = "#F5F5F1"),
        legend.position = "bottom",
        legend.justification = "centre",
        legend.background = element_rect(fill = "#F5F5F1"), 
        #panel is where you datapoints are
        panel.background = element_rect(fill = "#F5F5F1"),
        panel.grid.major = element_line(colour = "white"),
        panel.grid.minor = element_blank(),
         #area outside the panel
        plot.title = element_blank(),
        plot.background = element_rect(fill = "#F5F5F1"))
}

complete_per_2 %>% 
ggplot(aes(x = describe, y = estimated)) + 
  geom_point(aes(size = percent_desc, colour = phylum), alpha = 0.7) + 
  scale_size(range = c(2,10), name="Percent of species described") + 
# guides(colour = guide_legend(title = "Phylum")) +
  guides(size= guide_legend(override.aes=list(colour = "#bebea4"))) +
  # geom_text(aes(label = phylum), colour = "black", 
  #           size = 3, family = "Montserrat") +
  geom_text_repel(aes(label = phylum), colour = "black", 
                  size = 3, family = "Montserrat",
                  point.padding = 1) +
  xlab("Number of described species") + 
  ylab("Number of estimated species") +
  scale_x_log10(label = label_log()) +
  scale_y_log10(label = label_log()) +
  scale_colour_manual(values = c("#db9880", "#8D9BBC", "#B298BB", 
                               "#f0dd56", "#9ad9d1", "#eab35a",
                               "#CAA17C", "#A3B28D", "#465577",
                               "#9aa3b6", "#606672", "#b0d9f5",
                               "#d0d0d0"), guide = "none") +
  IA_theme()
```

https://www.rgbtohex.net/
https://pinetools.com/lighten-color